\textbf{Resilient Machine Learning Approaches \\ for Fast Risk Evaluation and Management \\ of Financial Portfolios and Variable Annuities}

### 2025-03-18 pre_private/pre.tex
12

% \setbeameroption{show notes}
% \setbeameroption{show notes on second screen=right}

\title[\textbf{Resilient Machine Learning Approaches for Fast Risk Evaluation and Management in Financial Portfolios and Variable Annuities}]{Efficient Machine Learning Approaches for Fast Risk Evaluation of VAs}

@@

\jointwork{Supervised by Prof. Tony Wirjanto and Prof. Mingbin Feng}
\conference{Thesis Defense, University of Waterloo}

@@

$$\rho(L) = \rho(L(X)), \;\;\; L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X}  $$

Involves two levels of Monte Carlo simulations:
\begin{itemize}
    \item Outer level: generates underlying risk factors (outer scenarios), $X_i \sim F_X$
    \item Inner level: generates scenario-wise samples of portfolio losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$
\end{itemize}

\textbf{Computationally expensive due to its nested structure.}

@@

@@

\section{Nested Simulation Procedures in Financial Engineering: A Selected Review}

@@

@@

\begin{frame}{Other Nested Simulation Procedures}

Subsequent works focus on improving the efficiency of nested simulation:
\begin{itemize}
    \item Regression-based~\citep{broadie2015risk}
    \item Kernel smoothing~\citep{hong2017kernel}
    \item Likelihood ratio~\citep{feng2020optimal}
    \item Kernel ridge regression~\citep{zhang2022sample}
\end{itemize}

@@

\textbf{Key ideas:} 
\begin{itemize}
    \item Pool inner replications from different outer scenarios 
    \item Use metamodeling techniques to approximate the inner simulation model
\end{itemize}

@@

In this thesis, we focus on procedures that use \textbf{supervised learning metamodels} to approximate the inner simulation model.

\begin{itemize}
    \item Treat the inner simulation as a black-box function
    \item Approximate $L(\cdot)$ with $\hat{L}^{\text{SL}}_{M, N}(\cdot)$
    \item Train with a set of feature-label pairs generated from the standard procedure:
    $$\{(X_i, \hat{L}_{N, i}) \vert i=1, \ldots, M, j=1, \ldots, N\}$$
    \item Use trained metamodel to make predictions for all $X \in \mathcal{X}$
\end{itemize}

There are \textbf{computational costs} associated with pooling inner replications.

\begin{frame}{Problem Statement}

Minimize mean squared error (MSE) of the estimator subject to total simulation budget:

Interested in convergence order as $\Gamma \to \infty$

@@

    \begin{table}
		\centering
		\begin{tabular}{l|c|c|c}
			\toprule
			\textbf{Procedures} & \textbf{Smooth $h$} & \textbf{Hockey-Stick $h$} & \textbf{Indicator $h$}  \\
			\midrule
			Standard Procedure	& \textcolor{red}{$\mathcal{O}(\Gamma^{-2/3})$} & \textcolor{red}{$\mathcal{O}(\Gamma^{-2/3})$} & $\mathcal{O}(\Gamma^{-2/3})$ \\
			\midrule
			Regression  & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1+\delta})$ & No Result \\
			\midrule
			Kernel Smoothing 	& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-\min(1, 4/(d+2))})$}  \\
			\midrule
			Kernel Ridge Regression  		& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-1})$} \\
			\midrule
			Likelihood Ratio  			& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-1})$} \\
			\bottomrule
		\end{tabular}
	\end{table}
    \vspace{10pt}
    \begin{itemize}
        \item We show the asymptotic convergence rates of the standard procedure for smooth and hockey-stick $h$.
        \item Only kernel smoothing depends on the asset dimension $d$.
    \end{itemize}

@@

\textbf{Observations:}
\begin{itemize}
\item Most literature focuses on the MSE of $\hat{\rho}$.
\item \citet{wang2022smooth} analyze convergence of absolute error in probabilistic order.
\end{itemize}

@@

@@

\begin{itemize}
    \item First result to draw connection between MSE and probabilistic order convergence.
    \item Applicable to any nested simulation procedure.
    \item Convergence in MSE implies convergence in probabilistic order.
\end{itemize}

@@

And their empirical convergence stable across different:
\begin{itemize}
    \item Risk measures
    \item Option types
    \item Asset dimensions
    \item Asset models (GBM vs. Heston)
    \item Regression bases (only for the regression-based procedure)
\end{itemize}

@@

@@

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure2a.png}
\end{figure}

@@

@@

@@

\begin{frame}{Sensitivity to Option Type}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure6a.png}
\end{figure}

\begin{itemize}
    \item Similar convergence patterns across different option types
    \item Regression and kernel smoothing show higher empirical rates for barrier options
\end{itemize}

\begin{frame}{Sensitivity to Risk Measure}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure8a.png}
\end{figure}

\begin{itemize}
    \item Convergence behavior consistent across different risk measures
    \item Regression-based method shows highest empirical convergence rates
\end{itemize}

\begin{frame}{Sensitivity to VaR/CVaR Level}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure9a.png}
\end{figure}

\begin{itemize}
    \item Regression-based method not sensitive to VaR/CVaR level
    \item Consistent performance across different levels
\end{itemize}

\begin{frame}{Sensitivity to Asset Model}

\begin{figure}
    \includegraphics[width=\textwidth]{../project1/figures/figure10a.png}
\end{figure}

\begin{itemize}
    \item Regression-based method insensitive to asset model (GBM vs. Heston)
    \item Consistent performance across different asset models
\end{itemize}

\begin{frame}{Computational Complexity}

    There are \textbf{computational costs} associated with pooling inner replications.

    \begin{itemize}
        \item Standard procedure: cost of estimating the optimal $M$ and $N$
        \item Regression: most efficient among metamodel-based procedures
        \item Kernel smoothing: costly distance calculations and cross-validation
        \item Likelihood ratio: No training, but costly weight calculations
        \item KRR: even more expensive than kernel smoothing
    \end{itemize}

@@

@@

\begin{frame}{Cost of Hyperparameter Tuning}

    \begin{figure}
        \includegraphics[width=\textwidth]{../project1/figures/figure12a.png}
        \caption{Cost of hyperparameter tuning for different procedures}
    \end{figure}

\begin{frame}{Cost of Model Fitting and Validation}

    \begin{figure}
        \includegraphics[width=\textwidth]{../project1/figures/figure12b.png}
        \caption{Cost of model fitting and validation for different procedures}
    \end{figure}

@@

@@

\section{Using Deep Neural Network Metamodels for High-Dimensional Nested Simulation}

\begin{frame}{From Options to Variable Annuities}

    Variable annuities (VAs) poses a challenge for nested simulation due to its \textbf{high-dimensional} and \textbf{complex payoff structure}.

    \begin{figure}[H]
            \includegraphics[width=0.33\textwidth]{./tikz/illustration_spns.pdf}
            \includegraphics[width=0.62\textwidth]{./tikz/illustration_mpns.pdf}
	\end{figure}

    \begin{itemize}
        \item Need to reconstruct a metamodeling-based nested simulation procedure
    \end{itemize}

@@

@@

\begin{frame}{Standard Nested Simulation for VAs}

Standard nested simulation for VAs is similar to the one for options.

\begin{itemize}
    \item Generate $M$ outer scenarios
    \item For each outer scenario,
    \begin{itemize}
        \item Perform $N$ inner simulations
        \item Estimate hedging loss $L_i$ with $\hat{L}_i$
    \end{itemize}
    \item Use estimated losses to calculate tail risk measures (e.g., $95\%$-CVaR)
\end{itemize}

\textbf{Observations:}
\begin{itemize}
    \item computational budget is limited;
    \item high-dimensional input space;
    \item only a \textbf{small} portion of scenarios are relevant when estimating \textbf{tail} risk measures.
\end{itemize}

@@

>>>>

\setbeameroption{show notes}
\setbeameroption{show notes on second screen=right}

\title[Resilient ML for Fast Risk Evaluation of VAs]{\textbf{Resilient Machine Learning Approaches \\ for Fast Risk Evaluation and Management \\ of Financial Portfolios and Variable Annuities}}

@@

\jointwork{Supervised by Prof. Tony Wirjanto and Prof. Mingbin Feng}
\conference{Thesis Defense, \\ University of Waterloo}

@@

$$\rho(L) = \rho(L(X)), \;\;\; L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X}.  $$

Involves two levels of Monte Carlo simulations:
\begin{itemize}
    \item Outer: underlying risk factors (outer scenarios), $X_i \sim F_X$
    \item Inner: scenario-wise losses (inner replications), $Y_{ij} \sim F_{Y|X_i}$
    \item Total simulation budget: $\Gamma = M \cdot N$
\end{itemize}

\vspace{10pt}
\textbf{Computationally expensive}

\note{In the context of quantitative risk management, nested simulation is used for risk evaluation of financial derivatives and insurance products. \\}
\note{The nested structure is due to the fact that the loss random variable is in the form of a conditional expectation of the portfolio loss given the underlying risk factors. \\}
\note{In our problems, the loss random variable $L$ depends on the risk factors $X$ and is the conditional expectation of the portfolio loss given $X$. \\}
\note{More specifically, $X$ is $d$-dimensional and $L$ is 1-dimensional. \\}
\note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: outer level generates underlying risk factors, and inner level generates scenario-wise samples of portfolio losses. \\}
\note{The nested structure makes the estimation computationally expensive. \\}
\note{In this thesis, we focus on examining and improving the efficiency of nested simulation procedures mostly using supervised learning metamodels.}

@@

\note{We consider different types of risk measures in this thesis. \\}
\note{The first three are in expectation form, and the last two are quantile-based risk measures. \\}
\note{The difference between the first three is the choice of the function $h$. \\}
\note{$h$ can be a smooth function, a hockey-stick function, or an indicator function. \\}
\note{The examples of risk measures are quadratic tracking error, mean excess loss, and probability of large loss. \\}
\note{The last two are value at risk and conditional value at risk, which are widely used in practice. \\}
\note{Note that the definition of CVaR requires the knowledge of the Value at Risk.}

@@

\section[Nested Simulation Procedures]{Nested Simulation Procedures in Financial Engineering: A Selected Review}

@@

\note{In our first project, we focus on comparing existing nested simulation procedures for different types of risk measures. \\}
\note{They differ in the way they estimate $L(X_i)$, the portfolio loss conditional on the risk factors $X_i$. \\}
\note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$. \\}
\note{The optimal growth order of $M$ and $N$ is found by \citet{gordy2010nested}. \\}
\note{For a growing total simulation budget $\Gamma$, $M$ should grow in the order of $\Gamma^{2/3}$, and $N$ should grow in the order of $\Gamma^{1/3}$. \\}
\note{For a finite-sample case, the bootstrap method is used to estimate the optimal $M$ and $N$ by \citet{zhang2021bootstrap}. \\}
\note{Since the standard procedure only uses the information from the same scenario, it is potentially \textbf{wasteful} use of budget. \\}
\note{Subsequent works focus on improving the efficiency of nested simulation by pooling inner replications from different outer scenarios.}

@@

% \begin{frame}{Other Nested Simulation Procedures}

% Subsequent works focus on improving the efficiency of nested simulation:
% \begin{itemize}
%     \item Regression-based~\citep{broadie2015risk}
%     \item Kernel smoothing~\citep{hong2017kernel}
%     \item Likelihood ratio~\citep{feng2020optimal}
%     \item Kernel ridge regression~\citep{zhang2022sample}
% \end{itemize}

% \vspace{10pt}

% \textbf{Key ideas:} 
% \begin{itemize}
%     \item Pool inner replications from different outer scenarios 
%     \item Use metamodels to approximate the inner simulation model
% \end{itemize}

% \note{Pooling can happen in different ways, and the key idea is to use the information from different outer scenarios to improve the efficiency of nested simulation. \\}
% \note{There are two main streams of research in this direction. \\}
% \note{The first stream is to use a supervised learning metamodel to approximate the simulation. \\}
% \note{A metamodel is a model of model, or a surrogate model for the simulation model. \\}
% \note{Here, the metamodel is used to approximate the inner simulation model, by treating it as a black-box function. \\}
% \note{The second stream is to use importance sampling to improve the efficiency of nested simulation. \\}
% \note{The likelihood ratio weights are used to weight the inner replications from different outer scenarios. \\}
% \note{This end up improving the efficiency of nested simulation as well.}

% \end{frame}

We focus on procedures that \textbf{pool} with \textbf{supervised learning metamodels}.

@@

\begin{itemize}
    \item Treat inner simulation as a black-box function
    \item Approximate $L(\cdot)$ with $\hat{L}^{\text{SL}}_{M, N}(\cdot)$
    \item Train with feature-label pairs generated by simulation:
    $$\{(X_i, \hat{L}_{N, i}) \vert i=1, \ldots, M, j=1, \ldots, N\}$$
    \item Use metamodel predictions to estimate risk measures
\end{itemize}

\vspace{10pt}
There are \textbf{computational costs} associated with pooling inner replications.

\note{A supervised learning based nested simulation procedure is implemented following these steps. \\}
\note{First, the user runs the standard nested simulation procedure to generate a set of outer scenarios and inner replications. \\}
\note{Then, the outer scenarios and inner sample means can be treated as features and labels. \\}
\note{Their relationship is then approximated by a supervised learning metamodel. \\}
\note{Finally, the trained metamodel is used to make predictions for all $X \in \mathcal{X}$. \\}
\note{In other words, instead of using the inner sample mean to estimate $L(X_i)$, we use the trained metamodel to make predictions of the portfolio loss. \\}
\note{These loss predictions are then used to calculate the risk measures of interest. \\}
\note{For most research in this area, the focus is on the convergence rate of the risk measure estimator in terms of the simulation budget. \\}
\note{However, in this thesis, we note that there are other important aspects to consider, such as the cost of pooling that may come from metamodel training and validation. }

@@

% \begin{frame}{Problem Statement}

% Minimize mean squared error (MSE) of the estimator subject to simulation budget $\Gamma$:

% \begin{align*}
% \min_{M, N} ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \\
% \text{ subject to } M \cdot N = \Gamma
% \end{align*}

% Interested in convergence order as $\Gamma \to \infty$

% \note{For a nested simulation procedure with a given total simulation budget $\Gamma$, the objective is to find the optimal $M$ and $N$ that minimizes the MSE of the estimator. \\}
% \note{Thus, in this thesis, we compare the asymptotic convergence rates of different nested simulation procedures using their MSE. \\}
% \note{Here, $\hat{\rho}_{M, N}$ is the risk measure estimator using the nested simulation procedure with $M$ outer scenarios and $N$ inner replications. \\}
% \note{We also consider the cost of pooling that may come from metamodel training and validation in our numerical experiments.}

% \end{frame}

@@

    \begin{table}
		\centering
		\begin{tabular}{l|c|c|c}
			\toprule
			\textbf{Procedures} & \textbf{Smooth $h$} & \textbf{Hockey-Stick $h$} & \textbf{Indicator $h$}  \\
			\midrule
			Standard Procedure	& \textcolor{color10_5}{$\mathcal{O}(\Gamma^{-2/3})$} & \textcolor{color10_5}{$\mathcal{O}(\Gamma^{-2/3})$} & $\mathcal{O}(\Gamma^{-2/3})$ \\
			\midrule
			Regression  & $\mathcal{O}(\Gamma^{-1})$ & $\mathcal{O}(\Gamma^{-1+\delta})$ & No Result \\
			\midrule
			Kernel Smoothing 	& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-\min(1, 4/(d+2))})$}  \\
			\midrule
			Kernel Ridge Regression\footnotemark  		& \multicolumn{3}{c}{\textcolor{color10_3}{$\mathcal{O}(\Gamma^{-1})$}} \\
			\midrule
			Likelihood Ratio  			& \multicolumn{3}{c}{$\mathcal{O}(\Gamma^{-1})$} \\
			\bottomrule
		\end{tabular}
	\end{table}
    \vspace{10pt}

\note{We start by comparing the asymptotic convergence rates of different nested simulation procedures. \\}
\note{These are the convergence rates of the MSE of the risk measure estimator when the total simulation budget $\Gamma$ goes to infinity, and when one follows the optimal growth order of $M$ and $N$. \\}
\note{The standard procedure has the same convergence rate of $\mathcal{O}(\Gamma^{-2/3})$ for all types of $h$ considered. The rates in red are not available in the original works but are derived in this thesis. \\}
\note{The regression-based procedure has $\mathcal{O}(\Gamma^{-1})$ convergence rate for smooth and hockey-stick $h$. \\}
\note{It is achieved by only allowing $M$ to grow in the order of $\Gamma^{1}$. In their experiments, $N$ is set to equal a value of $1$. \\}
\note{The kernel smoothing procedure is the only procedure that depends on the asset dimension $d$. \\}
\note{When risk factor $X$ is high-dimensional, the kernel smoothing procedure may converge slower than the standard procedure. \\}
\note{The kernel ridge regression procedure and likelihood ratio procedure have the same convergence rate as the regression-based procedure. \\}
\note{However, as we will see in the numerical experiments, their additional cost of pooling inner replications may offset their benefit of fast convergence rate. \\}
\note{Additionally for KRR, the authors analyze convergence of absolute error in probabilistic order instead of MSE.}

@@

@@

\note{In most theoretical works, the focus is on the convergence rate of the MSE of the risk measure estimator. \\}
\note{However, for KRR, the authors analyze convergence of absolute error in probabilistic order. \\}
\note{One of the contributions of this thesis is to bridge the gap between MSE and absolute error convergence. \\}
\note{Let's first define the convergence in MSE and the convergence in probabilistic order. \\}
\note{The convergence in MSE is the convergence of the MSE of the risk measure estimator to the true risk measure, that is, $\hat{\rho}_{\Gamma}$ minus $\rho$ squared. \\}
\note{The convergence in probabilistic order is the convergence of the absolute error of the risk measure estimator to the true risk measure, that is, $|\hat{\rho}_{\Gamma} - \rho|$ to 0 in probability. \\}
\note{We show that the convergence rate of the MSE of the risk measure estimator implies the convergence rate of the absolute error in probabilistic order. \\}
\note{We will also show that the converse is not necessarily true.}

@@

% \begin{frame}{Key Theoretical Results}

% \begin{block}{Theorem}
%     If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
% \end{block}

% \begin{itemize}
%     \item First result to draw connection between MSE and probabilistic order convergence.
%     \item Applicable to any nested simulation procedure.
%     \item Convergence in MSE implies convergence in probabilistic order.
% \end{itemize}

% \note{In the thesis, we provide a proof for the theorem above. \\}
% \note{Here I will give the intuition for the proof. \\}
% \note{The proof is based on the idea of splitting the expectation into two parts: the tail and the non-tail components. \\}
% \note{The non-tail component does not impact the type of convergence. \\}
% \note{Writing the tail component in an integral form shows that the convergence in MSE is stronger than the convergence in probabilistic order. \\}
% \note{The proof is provided in the thesis. \\}
% \note{Therefore, we have shown that the result of~\cite{wang2022smooth} is slightly weaker than the results shown in other works. }

% \end{frame}

@@

And their empirical convergence across different:
\begin{itemize}
    \item Risk measures
    \item Option types
    \item Asset dimensions
    \item Asset models (GBM vs. Heston)
    \item Regression bases (only for the regression-based procedure)
\end{itemize}

\note{Previously, we worked on the asymptotic convergence rates of different nested simulation procedures. \\}
\note{In practice, the total simulation budget is finite.}
\note{When the budget is finite, the theoretical convergence rate may not be the only thing we should consider. \\}
\note{We should also consider the cost of pooling itself. \\}
\note{The additional cost of pooling inner replications is not considered in the theoretical analysis of the previous works. \\}
\note{Neither it is mentioned in their numerical experiments. \\}
\note{More specifically, we have found that different research uses different numerical experiments to show the empirical rate of different procedures. \\}
\note{We aim to provide a fair and comprehensive analysis of the finite-sample performance of different nested simulation procedures. \\}
\note{The following numerical experiments test the empirical convergence rates of different nested simulation procedures across different risk measures, option types, asset dimensions, and asset models.}

@@

\note{This figure shows the performance of all 5 procedures in their estimation of the quadratic tracking error for the portfolio of European call options.}
\note{It is a log-log plot of the MSE of the estimator versus the total simulation budget $\Gamma$.}
\note{For each procedure, we run 1000 macro replications of Monte Carlo simulations with different total simulation budgets. \\}
\note{For each data point on the plot, 1000 independent replications of the procedure are used to estimate the MSE. \\}
\note{The slopes of the lines estimates the empirical convergence rates of the procedures. \\}
\note{In the legend records the slopes of the lines and the corresponding asymptotic convergence rates of the procedures. \\}
\note{In the most basic case, most procedures have their empirical convergence rates match their asymptotic convergence rates. \\}
\note{However, as we will see after, this is not the case for all experiments. \\}
\note{The following slides will show the sensitivity of the procedures to different factors. \\}

@@

% \begin{frame}{Sensitivity to Asset Dimension}

% \begin{figure}
%     \includegraphics[width=\textwidth]{../project1/figures/figure2a.png}
% \end{figure}

% \begin{itemize}
%     \item Standard, KRR, and likelihood ratio procedures are dimension-independent
%     \item Kernel smoothing and regression show sensitivity to dimension, but in different ways
% \end{itemize}

% \note{This figure shows the sensitivity of the procedures to the asset dimension. \\}
% \note{The asset dimension is the dimension of the risk factors $X$. \\}
% \note{Everything is the same as the previous figure, except that the asset dimension is varied from 1 to 2. \\}
% \note{The standard, regression, KRR, and likelihood ratio procedures are dimension-independent. \\}
% \note{The kernel smoothing procedure is sensitive to the asset dimension. \\}
% \note{Despite the fact that the kernel smoothing procedure has the same asymptotic convergence rate as before, it converges slower in practice. \\}

% \end{frame}

@@

\note{This figure shows the same experiment as the previous figure, but we further increase the asset dimension to 20. \\}
\note{The standard procedure is not affected by the asset dimension. \\}
\note{The kernel smoothing procedure actually converges faster than what its asymptotic convergence rate suggests. \\}
\note{The regression-based procedure is the only procedure that actually converges faster when the asset dimension is high. We will do a deeper dive into it in the following experiment. \\}
\note{It is also worth noting that the likelihood ratio and KRR procedures are dimension-independent. \\}
\note{While it is not shown in their empirical rate, due to their additional cost of pooling inner replications, we are not able to run these procedures when $\Gamma$ is large. \\}

@@

\note{To investigate the regression-based procedure, we further increase the total simulation budget $\Gamma$. \\}
\note{The figure shows the performance of the regression-based procedure in the estimation of the quadratic tracking error for the portfolio of European call options. \\}
\note{We separate different values of $\Gamma$ into two different parts. \\}
\note{The first part is when $\Gamma$ is small. \\}
\note{The second part is when $\Gamma$ is large. \\}
\note{The first part is when the regression-based procedure has a higher convergence rate than its asymptotic convergence rate. \\}
\note{The second part is when the regression-based procedure stabilizes and matches its asymptotic convergence rate. \\}
\note{In our experiments, we find that the regression-based procedure is very poor when $\Gamma$ is small. \\}
\note{It means that when we don't have enough data points, the regression-based procedure is particularly bad. \\}
\note{As we increase the total simulation budget $\Gamma$, the regression-based procedure improves fast, and eventually matches the asymptotic convergence rate. \\}

@@

% \begin{frame}{Sensitivity to Option Type}

% \begin{figure}
%     \includegraphics[width=\textwidth]{../project1/figures/figure7b.png}
% \end{figure}

% \begin{itemize}
%     \item Similar convergence patterns across different option types
%     \item Regression and kernel smoothing show higher empirical rates for barrier options
% \end{itemize}

% \note{This figure shows the performance of the procedures for a portfolio of 3 barrier options with a W-shaped payoff. \\}
% \note{This example is found in the regression-based procedure paper by broadie. It presents a case of complex payoffs for single asset dimension. \\}
% \note{Most procedures are not sensitive to the option type. \\}
% \note{The reason for kernel smoothing's MSE to increase at the right end of the plot is due to error in cross-validation of its bandwidth parameter. \\}
% \note{Due to the additional cost of cross-validation, we are not able to run it for every macro replication when the kernel smoothing procedure when $\Gamma$ is large. \\}
% \note{Instead, we use the same bandwidth parameter for all macro replications. \\}
% \note{A detailed explanation of this phenomenon is provided in the thesis. \\ }
% \note{We conducted a numerical experiment to show that the kernel smoothing procedure has sensitive cross-validation.}

% \end{frame}

% \begin{frame}{Sensitivity to Risk Measure}

%     \begin{figure}
%         \includegraphics[width=\textwidth]{../project1/figures/figure8a.png}
%     \end{figure}

%     \begin{itemize}
%         \item Convergence behavior consistent across different risk measures
%     \end{itemize}

% \note{This figure shows the performance of the procedures for estimating the mean excess loss for a portfolio of 10 geometric Asian options on 10 underlying assets. \\}
% \note{The mean excess loss is a risk measure that involves the tail of the distribution of the portfolio loss. \\}
% \note{Most procedures are consistent across different risk measures. \\}
% \note{The kernel smoothing procedure is the only procedure that is sensitive to the risk measure. }

% \end{frame}

% \begin{frame}{Sensitivity to VaR/CVaR Level}

%     \begin{figure}
%         \includegraphics[width=\textwidth]{../project1/figures/figure9a.png}
%     \end{figure}

%     \begin{itemize}
%         \item Regression-based method not sensitive to VaR/CVaR level
%         \item Consistent performance across different levels
%     \end{itemize}

%     \note{From our experiments, we find that the regression procedure is cheap to implement, and its performance is consistent across different experiments. \\}
%     \note{We shift our focus to the sentivity of regression-based procedure. First, we test its sensitivity to the VaR/CVaR level. \\}
%     \note{This figure shows the performance of the regression-based procedure for different VaR/CVaR levels. \\}
%     \note{The regression-based procedure is not sensitive to the VaR/CVaR level. \\}

% \end{frame}

% \begin{frame}{Sensitivity to Asset Model}

%     \begin{figure}
%         \includegraphics[width=\textwidth]{../project1/figures/figure10a.png}
%     \end{figure}

%     \begin{itemize}
%         \item Regression-based method insensitive to asset model (GBM vs. Heston)
%         \item Consistent performance across different asset models
%     \end{itemize}

%     \note{We further test the sensitivity of the regression-based procedure to the asset model. \\}
%     \note{This figure shows the performance of the regression-based procedure for different asset models. \\}
%     \note{The regression-based procedure is insensitive to the asset model. \\}

% \end{frame}

% \begin{frame}{Computational Complexity}

%     There are \textbf{computational costs} associated with pooling inner replications.

%     \begin{itemize}
%         \item Standard procedure: cost of estimating the optimal $M$ and $N$
%         \item Regression: most efficient among metamodel-based procedures
%         \item Kernel smoothing: costly distance calculations and cross-validation
%         \item Likelihood ratio: No training, but costly weight calculations
%         \item KRR: even more expensive than kernel smoothing
%     \end{itemize}

% \note{We have mentioned the cost of pooling inner replications multiple times. \\}
% \note{We now provide a detailed analysis of the computational complexity of different procedures. \\}
% \note{The standard procedure cannot be run without estimating the optimal $M$ and $N$. \\}
% \note{The regression procedure is the most efficient among metamodel-based procedures. \\}
% \note{The kernel smoothing procedure is costly due to the distance calculations and cross-validation. \\}
% \note{The likelihood ratio procedure does not require training, but the likelihood ratio weight calculations are costly. \\}
% \note{The KRR procedure is even more expensive than the kernel smoothing procedure due to the additional cost of the additional steps of ridge regression after the distance calculations. It also has more parameters to cross-validate. \\}

% \end{frame}

@@

    \note{This figure shows the total computation time for different procedures. \\}
    \note{It includes the time for both the simulation, training, validation, and everything else. \\}
    \note{The total computation time of the standard procedure does not increase fast with $\Gamma$. \\}
    \note{It is because the computation time of estimating the optimal $M$ and $N$ does not increase for larger $\Gamma$. \\}
    \note{The regression procedure and kernel smoothing procedure are the most efficient among metamodel-based procedures. \\}
    \note{Our implementation of the kernel smoothing procedure is efficient because we only run the cross-validation once for all macro replications. \\}
    \note{The likelihood ratio procedure and KRR procedure are more expensive due to their additional costs}
    \note{The likelihood ratio weight calculations increase quadratically with $\Gamma$. \\}
    \note{For KRR, the cost of cross-validation is so high that running it once still takes a very long time. \\}
    \note{In the thesis includes a detailed analysis of the computational complexity of different procedures in terms of $\Gamma$.}

@@

% \begin{frame}{Cost of Hyperparameter Tuning}

%     \begin{figure}
%         \includegraphics[width=\textwidth]{../project1/figures/figure12a.png}
%         \caption{Cost of hyperparameter tuning for different procedures}
%     \end{figure}

%     \note{We separate the additional computational cost into two parts: the cost of hyperparameter tuning and the cost of model fitting and validation. \\}
%     \note{The cost of hyperparameter tuning is the cost of running the cross-validation for the kernel smoothing procedure and KRR procedure. \\}
%     \note{$M$ and $N$ are hyperparameters for the standard procedure, so we also include the cost of estimating the optimal $M$ and $N$ in the figure. \\}
%     \note{From the figure, we can see that the cost of hyperparameter tuning contributes quite a lot to the total computation time. }
% \end{frame}

% \begin{frame}{Cost of Model Fitting and Prediction}

%     \begin{figure}
%         \includegraphics[width=\textwidth]{../project1/figures/figure12b.png}
%         \caption{Cost of model fitting and prediction for different procedures}
%     \end{figure}

%     \note{The cost of model fitting and prediction is the cost of fitting and using the metamodel. \\}
%     \note{We include the likelihood ratio procedure because using the likelihood ratio weights is similar to making predictions with a metamodel with fixed parameters. \\}
%     \note{We show that the regression-based and kernel-based procedures are very efficient in terms of model fitting and prediction. \\}
%     \note{Comparing the performance and the associated computational cost of different procedures, we find that the regression-based procedure is most cost-effective. \\}

% \end{frame}

@@

    \note{In our numerical experiemenct, we have shown that the regression-based procedure is the most cost-effective among all the procedures. \\}
    \note{It is robust and efficient to implement for limited budget sizes, and has fast empirical convergence for option portfolios. \\}
    \note{However, the regression-based procedure is not suitable for extremely high-dimensional risk factors or complex payoffs. \\}
    \note{The first reason is that it is hard to find a good regression basis for high-dimensional risk factors. It will involve a lot of feature engineering and expert knowledge. \\}
    \note{The second reason is that the regression-based procedure is not able to capture the nonlinearity in the payoff. \\}
    \note{In the next project, we will examine the performance of metamodel-based simulation procedures for variable annuities. \\}
    \note{This is where a neural network-based procedure can be more suitable as a form of automated feature engineering. }

@@

\section[Using DNNs for Nested Simulation]{Cutting Through the Noise: Using Deep Neural Network Metamodels for High-Dimensional Nested Simulation}

% \begin{frame}{From Options to Variable Annuities}

%     Variable annuities (VAs) poses a challenge for nested simulation due to its \textbf{high-dimensional} and \textbf{complex payoff structure}.

%     \vspace{10pt}

%     \begin{figure}[H]
%             \includegraphics[width=0.33\textwidth]{./tikz/illustration_spns.pdf}
%             \includegraphics[width=0.62\textwidth]{./tikz/illustration_mpns.pdf}
% 	\end{figure}

%     \vspace{10pt}

%     \begin{itemize}
%         \item Need to reconstruct a metamodeling-based nested simulation procedure
%     \end{itemize}

%     \note{Variable annuities poses a challenge for nested simulation due to its high-dimensional and complex payoff structure. \\}
%     \note{A regression-based procedure is not suitable. We need to reconstruct a metamodeling-based nested simulation procedure for VAs. \\}
%     \note{On the left is the illustration of our previous nested simulation procedure for options. \\}
%     \note{On the right is the illustration of the nested simulation procedure for VAs. \\}
%     \note{The main difference is that the payoff of VAs, when dynamic hedging is present, is a function of the entire path of the underlying asset. \\}
%     \note{In terms of metamodeling with machine learning, the feature is a time series of the underlying asset, and the label is the payoff of the VA with dynamic hedging. \\}

% \end{frame}

@@

    \note{The main difference of the standard nested simulation of VAs can be explained by this illustration. \\}
    \note{This is how the P\&L is estimated for one outer scenario. \\}
    \note{It starts at $t=0$ with a simulation to estimate the initial value of the VA contract and the initial hedge. Here we are using delta-hedging. \\}
    \note{This hedge gets carried forward and updated at each time period with another simulation. \\}
    \note{The P\&L is then estimated by adding up the hedging error at each time period to the initial value of the VA contract. \\}
    \note{All the simulation mentioned is a single set of inner simulations for one outer scenario. \\}
    \note{It is very expensive to run this standard nested simulation for VAs. \\}

@@

% \begin{frame}{Standard Nested Simulation for VAs}

% Standard nested simulation for VAs is similar to the one for options.

% \begin{itemize}
%     \item Generate $M$ outer scenarios
%     \item For each outer scenario,
%     \begin{itemize}
%         \item Perform $N$ inner simulations
%         \item Estimate hedging loss $L_i$ with $\hat{L}_i$
%     \end{itemize}
%     \item Use estimated losses to calculate tail risk measures (e.g., $95\%$-CVaR)
% \end{itemize}

% \vspace{10pt}

% \textbf{Observations:}
% \begin{itemize}
%     \item computational budget is limited;
%     \item high-dimensional input space;
%     \item only a \textbf{small} portion of scenarios are relevant when estimating \textbf{tail} risk measures.
% \end{itemize}

% \note{The standard nested simulation for VAs is similar to the one for options. \\}
% \note{First, we generate $M$ outer scenarios. \\}
% \note{For each outer scenario, we perform $N$ inner simulations to estimate the hedging loss $L_i$ with $\hat{L}_i$. \\}
% \note{Then, we use the estimated losses to calculate tail risk measures, such as a $95\%$-CVaR. \\}
% \note{The main difference is that the payoff of VAs, when dynamic hedging is present, is a function of the entire path of the underlying asset. \\}
% \note{In terms of metamodeling with machine learning, the feature is a time series of the underlying asset, and the label is the payoff of the VA with dynamic hedging. \\}
% \note{The computational budget is limited, and the input space is high-dimensional. \\}
% \note{Only a small portion of scenarios are relevant when estimating tail risk measures. \\}
% \note{In this project, we propose a metamodel-based nested simulation procedures to concentrate the simulation on the relevant scenarios. \\}

% \end{frame}

@@

\note{After numerical experiments, we find that the deep neural network metamodels are suitable for this problem. \\}
\note{We use LSTM for the sequential data. It provides accurate tail scenario identification and significant computational savings by budget concentration. \\}
\note{However, it is not transparent and interpretable. Many researchers are working on this topic. \\}
\note{This is where we can contribute to the research. \\}
\note{By using nested simulation as a data generating process, we can study the noise tolerance of DNNs. \\}
\note{The noise level in the training labels can be controlled by adjusting the simulation parameters. \\}
\note{By examining the performance of DNNs with different noise levels, we can provide direct evidence on the transparency and interpretability of DNNs. \\}
